Approximation as Differentiation notes

### 2025-03-04 notes/sec/grothendieck.tex
More consistent notation.
Introduce Fam(I,C) first.

\begin{definition}[Category of $I$-indexed families of objects]
For any set $I$ and any category $C$ write $\Fam(I,C)$ for the category where:
\begin{itemize}
\item objects are the $I$-indexed families of objects of $C$;
\item morphisms from $X$ to $Y$ are families of morphisms $f_i: X_i \to Y_i$ in $C$ for any $i \in I$.
\end{itemize}
\end{definition}

\noindent Equivalently $\Fam(I,C)$ is the functor category $\Func{I}{C}$, interpreting $I$ as a discrete
category.

\begin{definition}[Reindexing]
For any $f: I \to J$ the \emph{reindexing} functor $\reindex{-}{f}: \Fam(J,C) \to \Fam(I,C)$ sends any
$J$-indexed family $X$ to the $I$-indexed family $X[f]$ where $X[f]_i = X_{f(i)}$ for any $i \in I$, and
similarly for morphisms.
\end{definition}

\begin{definition}[$\Fam(-,C)$ functor]
$\Fam(-,C): \Set^{\op} \to \Cat$ is then the functor which sends any set $I$ to $\Fam(I,C)$ and any function
$f: I \to J$ to the functor $\reindex{-}{f}: \Fam(J,C) \to \Fam(I,C)$.
\end{definition}

@@

\begin{center}
\begin{tikzcd}
   {{[Y, Z]}} \tensor Y \arrow[dr, "\eval_{Y,Z}"] \\
   X \tensor Y \arrow[u, "\lambda_{X,Y,Z}(f) \tensor \id_Y"] \arrow[r, "f"'] & Z
\end{tikzcd}
\hspace{1cm}
\begin{tikzcd}
   \prod_{y \in \idx{Y}}\reindex{Z}{y \mapsto} \biprod \faml{Y}_y \arrow[dr, "\coprodM{\eval_{\prod_{\idx{Y}}}}{\faml{f}_i}"] \\
   \faml{X}_x \biprod \faml{Y}_y \arrow[u, "\lambda_{\prod_{\idx{Y}}}(y\;\mapsto\;\faml{f}_{x, y}\;\comp\;
\inj_{\faml{X}_x}) \biprod \id_{\faml{Y}_y}"] \arrow[r,
   "\faml{f}_{x,y}"'] & \faml{Z}_{\idx{f}(x,y)}
\end{tikzcd}
\end{center}

>>>>

@@

\begin{center}
\begin{tikzcd}
   {{[Y, Z]}} \tensor Y \arrow[dr, "\eval_{Y,Z}"] \\
   X \tensor Y \arrow[u, "\lambda_{X,Y,Z}(f) \tensor \id_Y"] \arrow[r, "f"'] & Z
\end{tikzcd}
\hspace{1cm}
\begin{tikzcd}
   \prod_{\idx{Y}}\reindex{\faml{Z}}{y' \mapsto \idx{f}(x,y')} \biprod \faml{Y}_y \arrow[dr,
   "\coprodM{\eval_{\prod_{\idx{Y}}}}{\faml{f}_x}"] \\
   \faml{X}_x \biprod \faml{Y}_y \arrow[u, "\lambda_{\prod_{\idx{Y}}}(y'\;\mapsto\;\faml{f}_{x, y'}\;\comp\;
\inj_{\faml{X}_x}) \biprod \id_{\faml{Y}_y}"] \arrow[r,
   "\faml{f}_{x,y}"'] & \faml{Z}_{\idx{f}(x,y)}
\end{tikzcd}
\end{center}
